Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ \smaller \textbf{{Istanbul version \YellowPaperVersionNumber}}

### 2021-06-13 Paper.tex
EIP-2200 original state is the same as the checkpoint state

We define the checkpoint state $\boldsymbol{\sigma}_0$:
\begin{eqnarray}
\boldsymbol{\sigma}_0 & \equiv & \boldsymbol{\sigma} \quad \text{except:} \\
\boldsymbol{\sigma}_0[S(T)]_{\mathrm{b}} & \equiv & \boldsymbol{\sigma}[S(T)]_{\mathrm{b}} - T_{\mathrm{g}} T_{\mathrm{p}} \\
\boldsymbol{\sigma}_0[S(T)]_{\mathrm{n}} & \equiv & \boldsymbol{\sigma}[S(T)]_{\mathrm{n}} + 1
\end{eqnarray}

@@

&&&& Let $\boldsymbol{\sigma}^0$ be the state if the current transaction were to revert (the ``original state''). \\
&&&& Let $v^0 = \boldsymbol{\sigma}^0[I_{\mathrm{a}}]_{\mathbf{s}}[\boldsymbol{\mu}_{\mathbf{s}}[0]]$ be the original value of the storage slot. \\

@@

G_{sload}  & \text{if} \quad v = v' \; \vee \; v^0 \neq v \\
G_{sset}   & \text{if} \quad v \neq v' \; \wedge \; v^0 = v \; \wedge \; v^0 = 0 \\
G_{sreset} & \text{if} \quad v \neq v' \; \wedge \; v^0 = v \; \wedge \; v^0 \neq 0 \\

@@

R_{sclear} & \text{if} \quad v \neq v' \; \wedge \; v^0 = v \; \wedge \; v' = 0 \\
r_{\text{dirtyclear}} + r_{\text{dirtyreset}} & \text{if} \quad v \neq v' \; \wedge \; v^0 \neq v \\

@@

-R_{sclear} & \text{if} \quad v^0 \neq 0 \; \wedge \; v = 0 \\
R_{sclear} & \text{if} \quad v^0 \neq 0 \; \wedge \; v' = 0 \\

@@

G_{sset} - G_{sload}   & \text{if} \quad v^0 = v' \; \wedge \; v^0 = 0 \\
G_{sreset} - G_{sload} & \text{if} \quad v^0 = v' \; \wedge \; v^0 \neq 0 \\

>>>>

We define the checkpoint state $\boldsymbol{\sigma}_0$:
\begin{eqnarray}
\linkdest{sigma_0}{}\boldsymbol{\sigma}_0 & \equiv & \boldsymbol{\sigma} \quad \text{except:} \\
\boldsymbol{\sigma}_0[S(T)]_{\mathrm{b}} & \equiv & \boldsymbol{\sigma}[S(T)]_{\mathrm{b}} - T_{\mathrm{g}} T_{\mathrm{p}} \\
\boldsymbol{\sigma}_0[S(T)]_{\mathrm{n}} & \equiv & \boldsymbol{\sigma}[S(T)]_{\mathrm{n}} + 1
\end{eqnarray}

@@

&&&& The checkpoint (``original'') state $\hyperlink{sigma_0}{\boldsymbol{\sigma}_0}$ is the state if the current transaction were to revert. \\
&&&& Let $v_0 = \boldsymbol{\sigma}_0[I_{\mathrm{a}}]_{\mathbf{s}}[\boldsymbol{\mu}_{\mathbf{s}}[0]]$ be the original value of the storage slot. \\

@@

G_{sload}  & \text{if} \quad v = v' \; \vee \; v_0 \neq v \\
G_{sset}   & \text{if} \quad v \neq v' \; \wedge \; v_0 = v \; \wedge \; v_0 = 0 \\
G_{sreset} & \text{if} \quad v \neq v' \; \wedge \; v_0 = v \; \wedge \; v_0 \neq 0 \\

@@

R_{sclear} & \text{if} \quad v \neq v' \; \wedge \; v_0 = v \; \wedge \; v' = 0 \\
r_{\text{dirtyclear}} + r_{\text{dirtyreset}} & \text{if} \quad v \neq v' \; \wedge \; v_0 \neq v \\

@@

-R_{sclear} & \text{if} \quad v_0 \neq 0 \; \wedge \; v = 0 \\
R_{sclear} & \text{if} \quad v_0 \neq 0 \; \wedge \; v' = 0 \\

@@

G_{sset} - G_{sload}   & \text{if} \quad v_0 = v' \; \wedge \; v_0 = 0 \\
G_{sreset} - G_{sload} & \text{if} \quad v_0 = v' \; \wedge \; v_0 \neq 0 \\
